---
title: "Normalizr"
author: "Stephen Johnson"
date: "''r Sys.Date()'"
output: rmarkdown::html_vignette
vignette: >
        %\VignetteIndexEntry{Normalizr}
        %\VignetteEngine{knitr::rmarkdown}
        \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(collapse = TRUE)
```

## Normalizing data

To normalize all data to 0-1:

$$
\operatorname{Data}_{out} = \frac{\operatorname{Data}_{in}}{\operatorname{Data}_{max}}
$$

This can be expanded to: 

$$
\operatorname{Data}_{out} = 0 + \frac{(\operatorname{Data}_{in} - \operatorname{Data}_{min}) \times (1 - 0)}{\operatorname{Data}_{max} - \operatorname{Data}_{min}}
$$

The general form is:

$$
\operatorname{Data}_{out} = \operatorname{Norm}_{min} + \frac{(\operatorname{Data}_{in} - \operatorname{Data}_{min}) \times (\operatorname{Norm}_{max} - \operatorname{Norm}_{min})}{\operatorname{Data}_{max} - \operatorname{Data}_{min}}
$$

```{r}
# source('R/normalizr.R')
```

## Normalize data using defaults

### If `normalize()` is called with a single argument, all the data are normalized to the range 0-1

```{r}
data <- 0:10
norm <- normalizr::normalize(data)
print(data)
print(norm)
```


## Normalize data to a range other than 0-1

### `normalize()` can be called with non-default values for `minNorm` and `maxNorm` to, e.g normalize to a percentage:

```{r}
data <- 0:10
norm <- normalizr::normalize(data, minNorm = 0, maxNorm = 100)
print(data)
print(norm)
```

### `minNorm` can be greater than `maxNorm` to invert the normalization

```{r}
data <- 0:10
norm <- normalizr::normalize(data, minNorm = 1, maxNorm = 0)
print(data)
print(norm)
```


### You can also specify `minData` and `maxData` values to consider

```{r}
data <- 0:10
norm <- normalizr::normalize(data, minData = 0, maxData = 5)
print(data)
print(norm)
```


### Or specify `minData`, `maxData`, `minNorm` and `maxNorm` for even more control

```{r}
data <- -5:5
norm <- normalizr::normalize(data, minData = 0, maxData = 5, minNorm = 0, maxNorm = 100)
print(data)
print(norm)
```
